\section{Expected Contribution}
\label{sec:expected_contribution}

We expect two different contributions from this research. 

First: the full decentralization of the introduced BTM. 
The bundle-trading market grants access to any given trade to the market dealer. 
This, again, necessitates the trust of the agents that it will use those resources
according to the overarching organizational goal. Due to the implementation 
of the market dealer by a smart contract, the technical implementation 
is publicly accessible. Moreover, all transactions of the market dealer 
to allocate the resources are transparent. Therefore, the behavior of the 
market dealer is comprehensible for every participant. Furthermore, it provides 
a high degree of security due to cryptographic encryption methods which are essential 
parts of the blockchain.

Second: the open \textit{Blockchain-based LEM Simulation (BLEMS)} itself. From the scientific perspective, 
the platform is relevant due to the removal of existing technical barriers 
for practitioners in using complex distributed ledgers technologies. 
Therefore the platform facilitates researchers without a deep 
technical background to use those DLTs and incentivizes them to design 
and test their artifacts by using this platform. 
Furthermore, from a business perspective, this research is 
relevant to policymakers and energy suppliers. The platform allows 
stakeholders to get a better understanding of the dynamics of decentralized 
LEM and enables the testing and evaluating of policy options and implications. 

\clearpage